 Casting multiple shadows: high-dimensional interactive data visualisation with tours and embeddings

### 2020-07-19 paper.Rmd
update paper

Our holistic framework is also useful in real data situations, as displayed
in our second case study. The tour when combined with t-SNE allowed us
to identify clusters, while giving us an idea of their orientation to 
each other. Moreover, we could visually inspect the separation clusters
using a tour on marker gene sets. This case study revealed some limitations
in using the **liminal** interface for larger datasets. First,
t-SNE avoids the crowding problem, points are seperated into distinct regions
on the graph canvas, while for the tour points are concentrated in the
center of the projection and become difficult to see. 
Second, as $n$ increases the animation becomes slower as there is more data passing from the server to the client.

>>>>

Our holistic framework is also useful in real data situations, as displayed
in our second case study. The tour when combined with t-SNE allowed us
to identify clusters, while giving us an idea of their orientation to 
each other. Moreover, we could visually inspect the separation of clusters
using a tour on marker gene sets. We see our approach as being valuable
to the single cell analyst who wants to make their embeddings more 
interpretable.

There are some limitations
in using the **liminal** interface for larger datasets. First,
t-SNE avoids the crowding problem, points are seperated into distinct regions
on the display canvas, while for the tour, points are concentrated in the
center of the projection and become difficult to see. 
Second, as $n$ increases the animation becomes slower as there is more data passing from the server to the client. Both of these issues could be mitigated
through alternate tour paths and displays. The recent work
by @Laa2020-wr is a promising area for further investigation, as well as
work from topological statistics [@Rieck2017-kk; @Genovese2017-iq].
